Evaluating FAIR Digital Object as a distributed object system

### 2023-01-30 latex/bibliography.tex
no "available at"

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-CJuBupCW}{}}%
. \emph{Available at} \href{https://blog.cloudflare.com/http-3-vs-http-2/}{\emph{https://blog.cloudflare.com/http-3-vs-http-2/}}

\leavevmode\vadjust pre{\hypertarget{ref-18P9txgeB}{}}%
. \emph{Available at} \href{https://www.rd-alliance.org/sites/default/files/Cordra.2022.pdf}{\emph{https://www.rd-alliance.org/sites/default/files/Cordra.2022.pdf}}

\leavevmode\vadjust pre{\hypertarget{ref-1BlxdxOwa}{}}%
14:00-17:00.ISO 16684-1:2019. \emph{Available at} \href{https://www.iso.org/standard/75163.html}{\emph{https://www.iso.org/standard/75163.html}} (accessed 24 January 2023b).

\leavevmode\vadjust pre{\hypertarget{ref-ikO7e0mh}{}}%
14:00-17:00.ISO/IEC 23009-1:2019. \emph{Available at} \href{https://www.iso.org/cms/render/live/en/sites/isoorg/contents/data/standard/07/93/79329.html}{\emph{https://www.iso.org/cms/render/live/en/sites/isoorg/contents/data/standard/07/93/79329.html}} (accessed 26 May 2022a).

\leavevmode\vadjust pre{\hypertarget{ref-11dInoyVF}{}}%
5-star Open Data. \emph{Available at} \href{http://5stardata.info/en/}{\emph{http://5stardata.info/en/}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1F8S9FeHf}{}}%
Bioschemas - Bioschemas. \emph{Available at} \href{http://bioschemas.org/}{\emph{http://bioschemas.org/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-n2f3TfoI}{}}%
Content negotiation - HTTP \textbar{} MDN. \emph{Available at} \href{https://developer.mozilla.org/en-US/docs/Web/HTTP/Content_negotiation}{\emph{https://developer.mozilla.org/en-US/docs/Web/HTTP/Content\_negotiation}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-o4h92LpS}{}}%
Data - W3C. \emph{Available at} \href{https://www.w3.org/standards/semanticweb/data}{\emph{https://www.w3.org/standards/semanticweb/data}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-zt8AAjcZ}{}}%
Data Catalog Vocabulary (DCAT) - Version 2. \emph{Available at} \href{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}{\emph{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}} (accessed 24 January 2023b).

\leavevmode\vadjust pre{\hypertarget{ref-lnH0hEuh}{}}%
Data Catalog Vocabulary (DCAT) - Version 2. \emph{Available at} \href{https://www.w3.org/TR/vocab-dcat-2/}{\emph{https://www.w3.org/TR/vocab-dcat-2/}} (accessed 26 May 2022a).

\leavevmode\vadjust pre{\hypertarget{ref-1EW4hLN8U}{}}%
Data Catalog Vocabulary (DCAT) - Version 3. \emph{Available at} \href{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}{\emph{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-6LvydTsC}{}}%
Data Information View. \emph{Available at} \href{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}{\emph{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-hKblceo6}{}}%
DCMI Metadata Terms. 2020. \emph{Available at} \href{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}{\emph{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-wAbZpOsr}{}}%
DCMI Metadata Terms. \emph{Available at} \href{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/}{\emph{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-BFMoe8FC}{}}%
Designing a Linked Data developer experience. 2018. \emph{Available at} \href{https://ruben.verborgh.org/blog/2018/12/28/designing-a-linked-data-developer-experience/}{\emph{https://ruben.verborgh.org/blog/2018/12/28/designing-a-linked-data-developer-experience/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-16uB3jxpa}{}}%
Digital Object Interface Protocol Version 1.0 \textbar{} DONA Foundation. \emph{Available at} \href{https://www.dona.net/doipv1doc}{\emph{https://www.dona.net/doipv1doc}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-68fzID2k}{}}%
DOI Handbook - Resolution. \emph{Available at} \href{https://www.doi.org/doi_handbook/3_Resolution.html}{\emph{https://www.doi.org/doi\_handbook/3\_Resolution.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-1H9iQhQYq}{}}%
DOI Resolution Documentation. \emph{Available at} \href{https://www.doi.org/factsheets/DOIProxy.html}{\emph{https://www.doi.org/factsheets/DOIProxy.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-xuQKRRx5}{}}%
DOIP and Examples --- Cordra documentation. \emph{Available at} \href{https://www.cordra.org/documentation/api/doip.html}{\emph{https://www.cordra.org/documentation/api/doip.html}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-p7nwRj8E}{}}%
DOIP API for HTTP Clients --- Cordra documentation. \emph{Available at} \href{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}{\emph{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-15EZ2D0Rm}{}}%
draft-bhutton-json-schema-00. \emph{Available at} \href{https://datatracker.ietf.org/doc/html/draft-bhutton-json-schema-00}{\emph{https://datatracker.ietf.org/doc/html/draft-bhutton-json-schema-00}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-nlH2rm1s}{}}%
draft-ietf-mediaman-suffixes-00 - Media Types with Multiple Suffixes. \emph{Available at} \href{https://datatracker.ietf.org/doc/draft-ietf-mediaman-suffixes/00/}{\emph{https://datatracker.ietf.org/doc/draft-ietf-mediaman-suffixes/00/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-Amit86Tp}{}}%
draft-ietf-quic-http-34. \emph{Available at} \href{https://datatracker.ietf.org/doc/html/draft-ietf-quic-http-34}{\emph{https://datatracker.ietf.org/doc/html/draft-ietf-quic-http-34}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-nyrPYHoP}{}}%
draft-kelly-json-hal-08. \emph{Available at} \href{https://datatracker.ietf.org/doc/html/draft-kelly-json-hal-08}{\emph{https://datatracker.ietf.org/doc/html/draft-kelly-json-hal-08}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-7szz7dwO}{}}%
FAIR Digital Object Framework Documentation. \emph{Available at} \href{https://fairdigitalobjectframework.org/}{\emph{https://fairdigitalobjectframework.org/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-DMEBhHID}{}}%
FAIR Digital Objects Forum \textbar. \emph{Available at} \href{https://fairdo.org/}{\emph{https://fairdo.org/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-XmUY0cZB}{}}%
FOAF Vocabulary Specification. \emph{Available at} \href{http://xmlns.com/foaf/spec/}{\emph{http://xmlns.com/foaf/spec/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1CvYRVhy2}{}}%
Handle.Net Registry. \emph{Available at} \href{https://www.handle.net/download_hnr.html}{\emph{https://www.handle.net/download\_hnr.html}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-14Utscfe4}{}}%
HTML Standard. \emph{Available at} \href{https://html.spec.whatwg.org/multipage/microdata.html}{\emph{https://html.spec.whatwg.org/multipage/microdata.html}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-13PaKBrZe}{}}%
Hydra W3C Community Group. \emph{Available at} \href{https://www.hydra-cg.com/}{\emph{https://www.hydra-cg.com/}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-rbG9uRKw}{}}%
Hypertext Style: Cool URIs don't change. \emph{Available at} \href{https://www.w3.org/Provider/Style/URI}{\emph{https://www.w3.org/Provider/Style/URI}} (accessed 26 May 2022a).

\leavevmode\vadjust pre{\hypertarget{ref-iME5l1kk}{}}%
Hypertext Style: Cool URIs don't change. \emph{Available at} \href{https://www.w3.org/Provider/Style/URI.html}{\emph{https://www.w3.org/Provider/Style/URI.html}} (accessed 26 May 2022b).

\leavevmode\vadjust pre{\hypertarget{ref-nW4HY8Nq}{}}%
"info" URI Registry (Frozen). \emph{Available at} \href{https://oclc-research.github.io/infoURI-Frozen/}{\emph{https://oclc-research.github.io/infoURI-Frozen/}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-by6CfOmv}{}}%
JSON-LD 1.1. \emph{Available at} \href{http://www.w3.org/TR/json-ld/}{\emph{http://www.w3.org/TR/json-ld/}} (accessed 26 May 2022b).

\leavevmode\vadjust pre{\hypertarget{ref-X5SWPqSU}{}}%
JSON-LD 1.1. \emph{Available at} \href{https://www.w3.org/TR/json-ld/}{\emph{https://www.w3.org/TR/json-ld/}} (accessed 26 May 2022a).

@@

\leavevmode\vadjust pre{\hypertarget{ref-xVJMmGVr}{}}%
Licenses \& Standards \textbar{} Open Source Initiative. \emph{Available at} \href{https://opensource.org/licenses}{\emph{https://opensource.org/licenses}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-OGXYtGZ8}{}}%
Linked Data - Design Issues. \emph{Available at} \href{https://www.w3.org/DesignIssues/LinkedData.html}{\emph{https://www.w3.org/DesignIssues/LinkedData.html}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-zlGYiuWC}{}}%
Linked Data Notifications. \emph{Available at} \href{https://www.w3.org/TR/ldn/}{\emph{https://www.w3.org/TR/ldn/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-QpDmajc4}{}}%
Linking Across Provenance Bundles. \emph{Available at} \href{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}{\emph{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-i9Ang0rM}{}}%
martinekuan.Web API design best practices - Azure Architecture Center. \emph{Available at} \href{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}{\emph{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1Gsq23e51}{}}%
NCBO BioPortal. \emph{Available at} \href{https://bioportal.bioontology.org/ontologies}{\emph{https://bioportal.bioontology.org/ontologies}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-k0AfCGzw}{}}%
OpenAPI Specification v3.1.0 \textbar{} Introduction, Definitions, \& More. \emph{Available at} \href{https://spec.openapis.org/oas/v3.1.0.html}{\emph{https://spec.openapis.org/oas/v3.1.0.html}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-ID1pTGry}{}}%
ORE Specification - Abstract Data Model. \emph{Available at} \href{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}{\emph{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-gtGuSevK}{}}%
ORE User Guide - Primer. \emph{Available at} \href{http://www.openarchives.org/ore/1.0/primer}{\emph{http://www.openarchives.org/ore/1.0/primer}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-1p4IWJpI}{}}%
OWL 2 Web Ontology Language Document Overview (Second Edition). \emph{Available at} \href{http://www.w3.org/TR/owl2-overview/}{\emph{http://www.w3.org/TR/owl2-overview/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-9T4j3N4e}{}}%
PROV-O: The PROV Ontology. \emph{Available at} \href{https://www.w3.org/TR/2013/REC-prov-o-20130430/}{\emph{https://www.w3.org/TR/2013/REC-prov-o-20130430/}} (accessed 24 January 2023a).

\leavevmode\vadjust pre{\hypertarget{ref-ZUgwvAHE}{}}%
PROV-O: The PROV Ontology. \emph{Available at} \href{https://www.w3.org/TR/prov-o/\#specializationOf}{\emph{https://www.w3.org/TR/prov-o/\#specializationOf}} (accessed 24 January 2023b).

\leavevmode\vadjust pre{\hypertarget{ref-16WGmCih8}{}}%
RDF 1.1 Primer. \emph{Available at} \href{http://www.w3.org/TR/rdf11-primer/}{\emph{http://www.w3.org/TR/rdf11-primer/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-ZwAcGQKY}{}}%
RDF Schema 1.1. \emph{Available at} \href{http://www.w3.org/TR/rdf-schema/}{\emph{http://www.w3.org/TR/rdf-schema/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-FKIF6ApB}{}}%
RDFa 1.1 Primer - Third Edition. \emph{Available at} \href{http://www.w3.org/TR/rdfa-primer/}{\emph{http://www.w3.org/TR/rdfa-primer/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-16wvFH4nh}{}}%
Resource Description Framework (RDF) Model and Syntax Specification. \emph{Available at} \href{https://www.w3.org/TR/1999/REC-rdf-syntax-19990222/}{\emph{https://www.w3.org/TR/1999/REC-rdf-syntax-19990222/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-eS5y9TRh}{}}%
ResourceSync Framework Specification - Table of Contents. \emph{Available at} \href{http://www.openarchives.org/rs/toc}{\emph{http://www.openarchives.org/rs/toc}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-F8VZ86hu}{}}%
Sandvine.Global Internet Phenomena Report 2022. \emph{Available at} \href{https://www.sandvine.com/global-internet-phenomena-report-2022}{\emph{https://www.sandvine.com/global-internet-phenomena-report-2022}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-10pzKCEUE}{}}%
Schema.org - Schema.org. \emph{Available at} \href{https://schema.org/}{\emph{https://schema.org/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-dKAekUjL}{}}%
Schema.org Actions - schema.org. \emph{Available at} \href{https://schema.org/docs/actions.html}{\emph{https://schema.org/docs/actions.html}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-kYjzRJ0H}{}}%
Semantic Web - XML2000 - slide "Architecture". \emph{Available at} \href{https://www.w3.org/2000/Talks/1206-xml2k-tbl/slide10-0.html}{\emph{https://www.w3.org/2000/Talks/1206-xml2k-tbl/slide10-0.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-YUzogaV}{}}%
Shape Expressions (ShEx) 2.1 Primer. \emph{Available at} \href{http://shex.io/shex-primer/}{\emph{http://shex.io/shex-primer/}} (accessed 26 May 2022).

>>>>

\hypertarget{refs}{}
%\begin{CSLReferences}{1}{0}
\begin{thebibliography}{9}

\bibitem[5stardata.info]{ref-11dInoyVF}
5-star Open Data. \href{http://5stardata.info/en/}{\emph{http://5stardata.info/en/}} (accessed 24 January 2023).

\end{thebibliography}

\leavevmode\vadjust pre{\hypertarget{ref-CJuBupCW}{}}%
. \href{https://blog.cloudflare.com/http-3-vs-http-2/}{\emph{https://blog.cloudflare.com/http-3-vs-http-2/}}

\leavevmode\vadjust pre{\hypertarget{ref-18P9txgeB}{}}%
. \href{https://www.rd-alliance.org/sites/default/files/Cordra.2022.pdf}{\emph{https://www.rd-alliance.org/sites/default/files/Cordra.2022.pdf}}

\leavevmode\vadjust pre{\hypertarget{ref-1BlxdxOwa}{}}%
14:00-17:00.ISO 16684-1:2019. \href{https://www.iso.org/standard/75163.html}{\emph{https://www.iso.org/standard/75163.html}} (accessed 24 January 2023b).

\leavevmode\vadjust pre{\hypertarget{ref-ikO7e0mh}{}}%
14:00-17:00.ISO/IEC 23009-1:2019. \href{https://www.iso.org/cms/render/live/en/sites/isoorg/contents/data/standard/07/93/79329.html}{\emph{https://www.iso.org/cms/render/live/en/sites/isoorg/contents/data/standard/07/93/79329.html}} (accessed 26 May 2022a).

\leavevmode\vadjust pre{\hypertarget{ref-11dInoyVF}{}}%
5-star Open Data. \href{http://5stardata.info/en/}{\emph{http://5stardata.info/en/}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1F8S9FeHf}{}}%
Bioschemas - Bioschemas. \href{http://bioschemas.org/}{\emph{http://bioschemas.org/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-n2f3TfoI}{}}%
Content negotiation - HTTP \textbar{} MDN. \href{https://developer.mozilla.org/en-US/docs/Web/HTTP/Content_negotiation}{\emph{https://developer.mozilla.org/en-US/docs/Web/HTTP/Content\_negotiation}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-o4h92LpS}{}}%
Data - W3C. \href{https://www.w3.org/standards/semanticweb/data}{\emph{https://www.w3.org/standards/semanticweb/data}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-zt8AAjcZ}{}}%
Data Catalog Vocabulary (DCAT) - Version 2. \href{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}{\emph{https://www.w3.org/TR/2020/REC-vocab-dcat-2-20200204/}} (accessed 24 January 2023b).

\leavevmode\vadjust pre{\hypertarget{ref-lnH0hEuh}{}}%
Data Catalog Vocabulary (DCAT) - Version 2. \href{https://www.w3.org/TR/vocab-dcat-2/}{\emph{https://www.w3.org/TR/vocab-dcat-2/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-1EW4hLN8U}{}}%
Data Catalog Vocabulary (DCAT) - Version 3. \href{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}{\emph{https://www.w3.org/TR/2022/WD-vocab-dcat-3-20220510/}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-6LvydTsC}{}}%
Data Information View. \href{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}{\emph{https://handle-esgf.dkrz.de/lp/21.14100/2fcf49d3-0608-3373-a47f-0e721b7eaa87}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-hKblceo6}{}}%
DCMI Metadata Terms. 2020. \href{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}{\emph{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/2020-01-20/}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-wAbZpOsr}{}}%
DCMI Metadata Terms. \href{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/}{\emph{https://www.dublincore.org/specifications/dublin-core/dcmi-terms/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-BFMoe8FC}{}}%
Designing a Linked Data developer experience. 2018. \href{https://ruben.verborgh.org/blog/2018/12/28/designing-a-linked-data-developer-experience/}{\emph{https://ruben.verborgh.org/blog/2018/12/28/designing-a-linked-data-developer-experience/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-16uB3jxpa}{}}%
Digital Object Interface Protocol Version 1.0 \textbar{} DONA Foundation. \href{https://www.dona.net/doipv1doc}{\emph{https://www.dona.net/doipv1doc}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-68fzID2k}{}}%
DOI Handbook - Resolution. \href{https://www.doi.org/doi_handbook/3_Resolution.html}{\emph{https://www.doi.org/doi\_handbook/3\_Resolution.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-1H9iQhQYq}{}}%
DOI Resolution Documentation. \href{https://www.doi.org/factsheets/DOIProxy.html}{\emph{https://www.doi.org/factsheets/DOIProxy.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-xuQKRRx5}{}}%
DOIP and Examples --- Cordra documentation. \href{https://www.cordra.org/documentation/api/doip.html}{\emph{https://www.cordra.org/documentation/api/doip.html}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-p7nwRj8E}{}}%
DOIP API for HTTP Clients --- Cordra documentation. \href{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}{\emph{https://www.cordra.org/documentation/api/doip-api-for-http-clients.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-15EZ2D0Rm}{}}%
draft-bhutton-json-schema-00. \href{https://datatracker.ietf.org/doc/html/draft-bhutton-json-schema-00}{\emph{https://datatracker.ietf.org/doc/html/draft-bhutton-json-schema-00}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-nlH2rm1s}{}}%
draft-ietf-mediaman-suffixes-00 - Media Types with Multiple Suffixes. \href{https://datatracker.ietf.org/doc/draft-ietf-mediaman-suffixes/00/}{\emph{https://datatracker.ietf.org/doc/draft-ietf-mediaman-suffixes/00/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-Amit86Tp}{}}%
draft-ietf-quic-http-34. \href{https://datatracker.ietf.org/doc/html/draft-ietf-quic-http-34}{\emph{https://datatracker.ietf.org/doc/html/draft-ietf-quic-http-34}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-nyrPYHoP}{}}%
draft-kelly-json-hal-08. \href{https://datatracker.ietf.org/doc/html/draft-kelly-json-hal-08}{\emph{https://datatracker.ietf.org/doc/html/draft-kelly-json-hal-08}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-7szz7dwO}{}}%
FAIR Digital Object Framework Documentation. \href{https://fairdigitalobjectframework.org/}{\emph{https://fairdigitalobjectframework.org/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-DMEBhHID}{}}%
FAIR Digital Objects Forum \textbar. \href{https://fairdo.org/}{\emph{https://fairdo.org/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-XmUY0cZB}{}}%
FOAF Vocabulary Specification. \href{http://xmlns.com/foaf/spec/}{\emph{http://xmlns.com/foaf/spec/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1CvYRVhy2}{}}%
Handle.Net Registry. \href{https://www.handle.net/download_hnr.html}{\emph{https://www.handle.net/download\_hnr.html}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-14Utscfe4}{}}%
HTML Standard. \href{https://html.spec.whatwg.org/multipage/microdata.html}{\emph{https://html.spec.whatwg.org/multipage/microdata.html}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-13PaKBrZe}{}}%
Hydra W3C Community Group. \href{https://www.hydra-cg.com/}{\emph{https://www.hydra-cg.com/}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-rbG9uRKw}{}}%
Hypertext Style: Cool URIs don't change. \href{https://www.w3.org/Provider/Style/URI}{\emph{https://www.w3.org/Provider/Style/URI}} (accessed 26 May 2022a).

\leavevmode\vadjust pre{\hypertarget{ref-iME5l1kk}{}}%
Hypertext Style: Cool URIs don't change. \href{https://www.w3.org/Provider/Style/URI.html}{\emph{https://www.w3.org/Provider/Style/URI.html}} (accessed 26 May 2022b).

\leavevmode\vadjust pre{\hypertarget{ref-nW4HY8Nq}{}}%
"info" URI Registry (Frozen). \href{https://oclc-research.github.io/infoURI-Frozen/}{\emph{https://oclc-research.github.io/infoURI-Frozen/}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-by6CfOmv}{}}%
JSON-LD 1.1. \href{http://www.w3.org/TR/json-ld/}{\emph{http://www.w3.org/TR/json-ld/}} (accessed 26 May 2022b).

\leavevmode\vadjust pre{\hypertarget{ref-X5SWPqSU}{}}%
JSON-LD 1.1. \href{https://www.w3.org/TR/json-ld/}{\emph{https://www.w3.org/TR/json-ld/}} (accessed 26 May 2022a).

@@

\leavevmode\vadjust pre{\hypertarget{ref-xVJMmGVr}{}}%
Licenses \& Standards \textbar{} Open Source Initiative. \href{https://opensource.org/licenses}{\emph{https://opensource.org/licenses}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-OGXYtGZ8}{}}%
Linked Data - Design Issues. \href{https://www.w3.org/DesignIssues/LinkedData.html}{\emph{https://www.w3.org/DesignIssues/LinkedData.html}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-zlGYiuWC}{}}%
Linked Data Notifications. \href{https://www.w3.org/TR/ldn/}{\emph{https://www.w3.org/TR/ldn/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-QpDmajc4}{}}%
Linking Across Provenance Bundles. \href{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}{\emph{https://www.w3.org/TR/2013/NOTE-prov-links-20130430/}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-i9Ang0rM}{}}%
martinekuan.Web API design best practices - Azure Architecture Center. \href{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}{\emph{https://learn.microsoft.com/en-us/azure/architecture/best-practices/api-design}} (accessed 24 January 2023).

@@

\leavevmode\vadjust pre{\hypertarget{ref-1Gsq23e51}{}}%
NCBO BioPortal. \href{https://bioportal.bioontology.org/ontologies}{\emph{https://bioportal.bioontology.org/ontologies}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-k0AfCGzw}{}}%
OpenAPI Specification v3.1.0 \textbar{} Introduction, Definitions, \& More. \href{https://spec.openapis.org/oas/v3.1.0.html}{\emph{https://spec.openapis.org/oas/v3.1.0.html}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-ID1pTGry}{}}%
ORE Specification - Abstract Data Model. \href{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}{\emph{http://www.openarchives.org/ore/1.0/datamodel\#Proxies}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-gtGuSevK}{}}%
ORE User Guide - Primer. \href{http://www.openarchives.org/ore/1.0/primer}{\emph{http://www.openarchives.org/ore/1.0/primer}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-1p4IWJpI}{}}%
OWL 2 Web Ontology Language Document Overview (Second Edition). \href{http://www.w3.org/TR/owl2-overview/}{\emph{http://www.w3.org/TR/owl2-overview/}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-9T4j3N4e}{}}%
PROV-O: The PROV Ontology. \href{https://www.w3.org/TR/2013/REC-prov-o-20130430/}{\emph{https://www.w3.org/TR/2013/REC-prov-o-20130430/}} (accessed 24 January 2023a).

\leavevmode\vadjust pre{\hypertarget{ref-ZUgwvAHE}{}}%
PROV-O: The PROV Ontology. \href{https://www.w3.org/TR/prov-o/\#specializationOf}{\emph{https://www.w3.org/TR/prov-o/\#specializationOf}} (accessed 24 January 2023b).

\leavevmode\vadjust pre{\hypertarget{ref-16WGmCih8}{}}%
RDF 1.1 Primer. \href{http://www.w3.org/TR/rdf11-primer/}{\emph{http://www.w3.org/TR/rdf11-primer/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-ZwAcGQKY}{}}%
RDF Schema 1.1. \href{http://www.w3.org/TR/rdf-schema/}{\emph{http://www.w3.org/TR/rdf-schema/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-FKIF6ApB}{}}%
RDFa 1.1 Primer - Third Edition. \href{http://www.w3.org/TR/rdfa-primer/}{\emph{http://www.w3.org/TR/rdfa-primer/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-16wvFH4nh}{}}%
Resource Description Framework (RDF) Model and Syntax Specification. \href{https://www.w3.org/TR/1999/REC-rdf-syntax-19990222/}{\emph{https://www.w3.org/TR/1999/REC-rdf-syntax-19990222/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-eS5y9TRh}{}}%
ResourceSync Framework Specification - Table of Contents. \href{http://www.openarchives.org/rs/toc}{\emph{http://www.openarchives.org/rs/toc}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-F8VZ86hu}{}}%
Sandvine.Global Internet Phenomena Report 2022. \href{https://www.sandvine.com/global-internet-phenomena-report-2022}{\emph{https://www.sandvine.com/global-internet-phenomena-report-2022}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-10pzKCEUE}{}}%
Schema.org - Schema.org. \href{https://schema.org/}{\emph{https://schema.org/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-dKAekUjL}{}}%
Schema.org Actions - schema.org. \href{https://schema.org/docs/actions.html}{\emph{https://schema.org/docs/actions.html}} (accessed 26 May 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-kYjzRJ0H}{}}%
Semantic Web - XML2000 - slide "Architecture". \href{https://www.w3.org/2000/Talks/1206-xml2k-tbl/slide10-0.html}{\emph{https://www.w3.org/2000/Talks/1206-xml2k-tbl/slide10-0.html}} (accessed 24 January 2023).

\leavevmode\vadjust pre{\hypertarget{ref-YUzogaV}{}}%
Shape Expressions (ShEx) 2.1 Primer. \href{http://shex.io/shex-primer/}{\emph{http://shex.io/shex-primer/}} (accessed 26 May 2022).

\leavevmode\vadjust pre{\hypertarget{ref-GDrm9dgX}{}}%
Shapes Constraint Language (SHACL). \href{https://www.w3.org/TR/shacl/}{\emph{https://www.w3.org/TR/shacl/}} (accessed 26 May 2022).
